### 2022-08-26 manuscript.Rmd
Cache figures

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = FALSE,
  mixed_models = FALSE,
  control_analysis = FALSE
)

@@

```{r, fig1, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

@@

```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", eval=TRUE}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed"
)
```

>>>>

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = FALSE,
  mixed_models = FALSE,
  control_analysis = FALSE,
  figures = FALSE
)

@@

```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-2-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

@@

```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-s1-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed"
)
```
